%-------------------------
% Resume in Latex
% Author : Charoen Chaweechan
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Charoen Chaweechan} \\ \vspace{1pt}
    Bangkok, Thailand, 10150 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +66 84263 6259 ~ \href{mailto:ch.chaweechan@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ch.chaweechan@gmail.com}} ~ 
    \href{https://linkedin.com/in/charoen-software-engineer/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/charoen-software-engineer}}  ~
    \href{https://github.com/chrnixr}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/chrnixr}}
    \vspace{-8pt}
\end{center}

%-----------About ME-----------
\section{About Me}
  \resumeSubHeadingListStart
    \resumeItem{Senior Software Engineer with 8+ years of experience designing and building scalable backend systems and highavailability architectures within the fintech domain. Specialized in microservices and event-driven systems, with a strong track record of delivering reliable, highperformance platforms supporting large-scale financial operations. Proven ability to architect and integrate backend services that handle high-volume transactions while ensuring security, fault tolerance, and system stability. At Krungsri Nimble, contributed to the architecture and development of a digital banking platform serving over 199K users, maintaining zero downtime and zero critical production incidents. Experienced in backend integration, distributed systems, and production reliability under mission-critical environments.}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {King Mongkut's Institute of Technology Ladkrabang}{May. 2011 -- May 2015}
      {Bachelor of Engineering (B.Eng.) Software Engineering (International Program)}{Bangkok, Thailand}
  \resumeSubHeadingListEnd

%----------KEY achievements ------
\section{Key achievements}
  \resumeItemListStart
    \resumeItem{Supported digital banking platform serving \textbf{199K+ users and 37K+ monthly active clients}.}
    \resumeItem{Achieved zero downtime and zero P1/P2 incidents in production during 2025.}
    \resumeItem{Built enterprise financial systems supporting \textbf{28K+ clients}.}
    \resumeItem{Delivered mission-critical transaction services for banking operations.}
  \resumeItemListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Krungsri Nimble}{Dec 2020 -- Present}
      {Senior Software Engineer}{Bangkok, Thailand}
      \resumeItemListStart
        \resumeItem{Designed and contributed to \textbf{backend architecture and microservices integration} for a large-scale digital banking platform.}
        \resumeItem{Built and supported systems serving \textbf{199K+ users and 37K+ monthly active clients}.}
        \resumeItem{Developed and integrated \textbf{high-volume financial transaction services} including transfers/swift transfer, QR payments, and payroll processing.}
        \resumeItem{Implemented \textbf{event-driven architecture patterns} to improve system scalability and fault tolerance.}
        \resumeItem{Collaborated on \textbf{secure backend integrations} supporting enterprise financial operations for \textbf{28K+ clients}.}
        \resumeItem{Achieved \textbf{zero downtime and zero P1/P2 incidents} in production during 2025.}
        \resumeItem{Worked closely with cross-functional teams to ensure \textbf{robust system design and production stability}.}
      \resumeItemListEnd

    \resumeSubheading
      {KBTG}{Jan 2019 -- Nov 2020}
      {Software Engineer}{Bangkok, Thailand}
      \resumeItemListStart
        \resumeItem{Developed \textbf{Credit Bureau Integration System (KCBS)} supporting both batch and real-time processing.}
        \resumeItem{Enabled seamless integration with National Credit Bureau (NCB) systems for loan approval workflows.}
        \resumeItem{Built \textbf{Income Verification Platform (KVI)} to automate borrower financial validation.}
        \resumeItem{Improved processing efficiency and accuracy for loan decision-making.}
        \resumeItem{Implemented data import, calculation rules, and reporting (Excel/PDF export).}
        \resumeItem{Managed production releases with \textbf{zero rollback incidents}.}
        \resumeItem{Established monitoring and incident handling processes to maintain system reliability.}
    \resumeItemListEnd

    \resumeSubheading
      {Samart Comtech Co., Ltd.}{Apr 2017 -- Dec 2019}
      {Software Engineer}{Bangkok, Thailand}
      \resumeItemListStart
        \resumeItem{Designed and developed \textbf{Contract Lifecycle Management System} for enterprise back-office operations.}
        \resumeItem{Built automated \textbf{multi-stage email notification workflows} for contract expiration tracking.}
        \resumeItem{Reduced manual workload through system automation and alerting mechanisms.}
        \resumeItem{Implemented \textbf{file attachment and contract tracking features}.}
        \resumeItem{Delivered \textbf{Excel-based reporting tools} to enhance operational visibility.}
    \resumeItemListEnd

    \resumeSubheading
      {Augmentis (Thailand) Ltd.}{Jun 2015 -- Mar 2017}
      {Software Engineer}{Bangkok, Thailand}
      \resumeItemListStart
        \resumeItem{Translated business requirements into scalable internal web applications.}
        \resumeItem{Developed enterprise solutions to streamline workflows and improve operational efficiency.}
        \resumeItem{Collaborated with stakeholders to deliver customized business systems.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C\#, TypeScript/JavaScript, HTML, CSS, SQL} \\
     \textbf{Cloud \& Infrastructure}{:AWS, Azure, CI/CD} \\
     \textbf{Technologies/Frameworks}{:  .Net Core, .Net Framework, Spring Boot, Docker, MS SQL, PostgreSQL, Git, Dynatrace,
GitHub Copilot, Claude Code} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Krungsri Biz Online / Krungsri Biz Mobile}}{}
          \resumeItemListStart
            \resumeItem{Mobile banking applications for SME and corporate clients.}
            \resumeItem{Delivered secure and scalable financial transaction capabilities.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{CBDC Krungsri (Deprecated)}}{}
          \resumeItemListStart
            \resumeItem{Flutter-based application for Central Bank Digital Currency (CBDC) transactions.}
            \resumeItem{Wallet Share feature (Main/Sub wallet management).}
            \resumeItem{Auto Currency Conversion (CBDC \textrightarrow THB) at the end of the day.}
          \resumeItemListEnd 
          \vspace{-13pt}

          \resumeProjectHeading
          {\textbf{KBank Credit Bureau System (KCBS)}}{}
          \resumeItemListStart
            \resumeItem{Supports National Credit Bureau (NCB) inquiries via both Batch and Online applications.}
            \resumeItem{Batch application is used for the Credit Review module.}
            \resumeItem{Online application is available on both Web and Windows platforms for new credit request modules.}
          \resumeItemListEnd
          \vspace{-13pt}

          \resumeProjectHeading
          {\textbf{KBank Verify Income (KVI)}}{}
          \resumeItemListStart
            \resumeItem{Web application for verifying borrowers' income to support credit decision-making.}
            \resumeItem{Supports statement data import from both KBank and non-KBank accounts.}
            \resumeItem{Calculates customer income based on predefined rules used in the bank's loan approval process.}
            \resumeItem{Allows exporting income summaries in Excel or PDF format.}
          \resumeItemListEnd
          \vspace{-13pt}

          \resumeProjectHeading
          {\textbf{Contract Alert System}}{}
          \resumeItemListStart
            \resumeItem{Web application for sending email alerts when contracts or documents are approaching their expiration dates, covering companies under SAMART Corporation.}
            \resumeItem{Supports multiple reminder schedules per document
and allows file attachments for each contract record.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}

 %-----------CERTIFICATIONS---------------
\section{Certifications}
    \resumeSubHeadingListStart
        \item[]
            \resumeItemListStart
                \resumeItem{Azure Data Fundamentals  $|$ Microsoft Certified}
                \resumeItem{Google People Management Essentials}
                \resumeItem{AI Practitioner $|$ AWS Certified}
            \resumeItemListEnd        
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}
